\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{graphicx}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = blue,
            citecolor = black,
            anchorcolor = blue]{hyperref}
\usepackage{amsmath,amssymb,amsfonts, mathtools}
\usepackage{algorithmic}
\usepackage{textcomp}
\usepackage{lipsum}                     
\usepackage{xargs}                      
\usepackage[pdftex,dvipsnames, table]{xcolor}  
\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{subcaption}
\usepackage{stfloats}
\usepackage{bbm}
\usepackage[
backend=biber,
style=numeric,
sorting=ynt
]{biblatex}
\addbibresource[]{misc/references.bib}

\rowcolors{2}{gray!10}{white}

\newcommand{\titlecol}{\cellcolor{gray!30}}

% 
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommandx{\unfinished}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}

\begin{document}
\title{Security Analysis of Android application\\
{\LARGE System Security}}

\author{\IEEEauthorblockN{Morten Lyng Rosenquist}
\IEEEauthorblockA{\textit{Faculty of Technical Sciences} \\
\textit{Aarhus University}\\
Aarhus, Denmark \\
201706031 \\ \\ 
\today
}
}

\maketitle

\begin{abstract}
In this report a preliminary security analysis is performed on an Android mobile application. GulOgGratis, a public Marketplace, is the targeted application. Several security properties are essential when managing such a platform. The users' data need to be handled properly and the application must respect the users' privacy. Several improvements was found by investigating decompiled source code and network traffic. Measures were not taken to harden adversaries gaining insight of the applications functionality. However, no severe vulnerability was found. Users' actions are monitored heavily and primarily used to personalize advertisements.
\end{abstract}

\begin{IEEEkeywords}
Security Analysis, Android Security, Software Security, Network Security, man-in-the-middle
\end{IEEEkeywords}

\section{Introduction}
\input{contents/introduction.tex}

\section{Software Security}
\input{contents/software-security.tex}

\section{Network Security}
\input{contents/network-security.tex}

\section{Authentication}
\input{contents/authentication.tex}

\section{Privacy}
\input{contents/privacy.tex}

\section{Discussion}
\input{contents/discussion.tex}

\section{Conclusion}
\input{contents/conclusion.tex}

\printbibliography
\end{document}